Untrusted B2B Collaboration using the Blockchain

### 2018-07-11 paper/paper.tex
rearrange and add more figures

@@

@@

@@

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig/system_diagram.eps}
\caption{The architecture of our design.} \label{fig1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{fig/initialization.eps}
\caption{An initialization process.} \label{fig2}
\end{figure}

@@

\subsection{Contracts}

@@

>>>>

factory (maps to process)
creates instance (maps to process instance)
also access contract for user rights management

@@

access contract API

@@

Figure~\ref{fig:system_diagram} shows the architecture of our design.

\begin{figure}
    \begin{center}
        \includegraphics[width=200px]{fig/system_diagram.eps}
    \end{center}
    \caption{The architecture of our design.} \label{fig:system_diagram}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=200px]{fig/initialization.eps}
    \end{center}
    \caption{An initialization process.} \label{fig:initialization}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=200px]{fig/instance_creation.eps}
    \end{center}
    \caption{An initialization process.} \label{fig:instance_creation}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=200px]{fig/event_sending.eps}
    \end{center}
    \caption{An initialization process.} \label{fig:event_sending}
\end{figure}

@@

\subsection{Contracts}
\cite{xu2018pattern}

factory
instance

\subsubsection{Access Contract}

we chose mapping approach
other approaches part of further work, e.g. token based

@@

node-js command line tool using vorpal
commands trigger blockchain calls using web3
